This is an example of article title

### 2025-10-28 paper/paper.tex
start an example

\section{An example how to use {\texttt{LieGroups.jl}}}\label{sec:Example}

{\color{red}TODO: Brainstorm over one or two examples with code.}
\input{bib.tex}
\end{document}
%
% ------------------------------------------------------------------------------------------
%

>>>>

\section{An example how to use {\texttt{LieGroups.jl}}}%
\label{sec:Example}

In this section, we provide examples of how to use the {\texttt{LieGroups.jl}} package in Julia.

\subsection{A Beziér curve on a Lie group}

In the first example we illustrate how to construct and plot a Beziér curve on a Lie group, here the special Euclidean group \(\mathrm{SE}(2)\).

We first can generalize the de-Casteljau algorithm for Beziér curves to Lie groups by replacing the linear interpolation step with using the exponential and logarithmic map.

\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:deCasteljauLieGroup},
    caption={de-Casteljau algorithm on a Lie group.}
]
using LieGroups, ManifoldsBase, RecursiveArrayTools
using CairoMakie
"""
    deCasteljauLieGroup(G, cp, t)

Evaluate the Beziér curve at parameter `t` given
a vector of control points `cp` on the Lie group `G`.
"""
function deCasteljauLieGroup(
        G::AbstractLieGroup, cp::Vector{P}, t::Real
    ) where {P}
    n = length(cp)
    points = [copy(G, g) for g in cp]
    for r in 1:n-1
        for i in 1:n-r
            X = log(G, points[i], points[i+1])
            exp!(G, points[i], points[i], t * X)
        end
    end
    return points[1]
end
\end{lstlisting}

In Algorithm~\ref{lst:deCasteljauLieGroup}, define the general de-Casteljau algorithm on a Lie group \verb|G|, given a vector of control points \verb|cp| and a parameter \verb|t| in \([0,1]\).

We can now compare the algorithm on the Lie group \(\mathrm{SE}(2)\) with the corresponding Bézier curve on the (direct) product Lie group $\mathrm{SO}(2) \times \mathbb{R}^2$. Denote by $R_\alpha$ the rotation matrix in \(\mathrm{SO}(2)\) for an angle \(\alpha\in[0,2\pi)\). Then we consider the control points
\begin{align*}
    g_1 &= \begin{pmatrix} R_0 & \begin{pmatrix} 0 \\ 0 \end{pmatrix} \\
    0 & 1 \end{pmatrix}, \quad
g_2 = \begin{pmatrix} R_{\pi/2} & \begin{pmatrix} 1 \\ 0 \end{pmatrix} \\
    0 & 1 \end{pmatrix}, \\
g_3 &= \begin{pmatrix} R_{\pi} & \begin{pmatrix}
    1 \\ 1 \end{pmatrix} \\
0 & 1 \end{pmatrix}, \quad
\end{align*}

As data we take the points

\subsection{A simple forward Euler integration on a Lie group.}

For more details on solving differential equations on Lie groups in Julia, see
\verb|ManifoldDiffEq.jl|.

{\color{red}TODO: Provide code for de-Casteljau algorithm on Lie groups.}

{\color{red}TODO: Brainstorm over one or two examples with code.}

\input{bib.tex}
\end{document}
%
% ------------------------------------------------------------------------------------------
%
